\section{INTRODUCTION}
	
%	Unmanned ground vehicles (UGV) that operate without on-board operators have been used for many applications that are inconvenient, dangerous, or impossible to human. 
	Estimation using a group of networked UGVs has been widely utilized to collectively measure environment status \cite{hedrick2011tools}, such as intruder detection \cite{chamberland2007wireless}, signal source seeking \cite{atanasov2015distributed}, and pollution field estimation \cite{madhag2017distributed},
	due to its merits on low cost, high efficiency, and good reliability.
	The commonly adopted estimation approaches include the Kalman Filter, extended Kalman filter, and particle filter \cite{thrun2005probabilistic}, and
%	Several techniques have been developed for distributed estimation, including distributed linear Kalman filter (DKF) \cite{2005distributed}, distributed extended Kalman filter \cite{madhavan2004distributed}, and distributed particle filter \cite{gu2007distributed}. 
	the most generic scheme might be the Bayesian filter because of its applicability for nonlinear systems with arbitrary noise distributions \cite{bandyopadhyay2014distributed,julian2012distributed}.
	In fact, a Bayesian filter can be reduced to different methods in certain conditions.
	For example, under the assumption of linearity and Gaussian noise, a Bayesian filter can be reduced to the Kalman filter \cite{chen2003bayesian}; 
	\textcolor{\revcol}{for general nonlinear systems, a Bayesian filter can be numerically implemented as a particle filter \cite{chen2003bayesian}}.
%	due to the advantage in computation \cite{chen2003bayesian}.
	Because of this generality, this study focuses on its networked variant, \textcolor{\revcol}{and use it for tracking targets via local communication between neighboring UGVs.} % under dynamically changing interaction topologies.
	
	The interaction topology \cite{zheng2016stability,zheng2017distributed} plays a central role on the design of networked Bayesian filter, of which two types are widely investigated in literature: centralized filters and distributed filters.
	In the former, local statistics estimated by each agent is transmitted to a single fusion center, where a global posterior distribution is calculated at each filtering cycle \cite{zuo2006bandwidth,vemula2006target}. 
	In the latter, each agent individually executes distributed estimation and the agreement of local estimates is achieved by certain consensus strategies \cite{jadbabaie2003coordination,ren2005consensus,olfati2007consensus}.
	In general, the distributed filters are more suitable in practice since they do not require a fusion center with powerful computation capability and are more robust to changes in network topology and link failures. 
	So far, the distributed filters have two mainstream schemes in terms of the transmitted data among agents, i.e., \textit{statistics dissemination} (SD) and \textit{measurement dissemination} (MD). 
	In the SD scheme, each agent exchanges statistics, such as posterior distributions and likelihood functions, within neighboring agents \cite{hlinka2013distributed}. 
	In the MD scheme, instead of exchanging statistics, each agent sends sensor measurements to neighboring agents. 
	
%	The pioneering work of statistics dissemination scheme can date back to the 80s of last century \todohere{reference}. 
%	Later, \todohere{reference} have considerably advanced the study of this scheme in the field of distributed estimation. 
	The statistics dissemination scheme has been widely investigated during the last decade, especially in the field of signal processing, network control, and robotics.
	Madhavan et al. (2004) presented a distributed extended Kalman filter for nonlinear systems \cite{madhavan2004distributed}. 
	This filter was used to generate local terrain maps by using pose estimates to combine elevation gradient and vision-based depth with environmental features. 
	Olfati-Saber (2005) proposed a distributed linear Kalman filter (DKF) for estimating states of linear systems with Gaussian process and measurement noise \cite{2005distributed}. 
	Each DKF used additional low-pass and band-pass consensus filters to compute the average of weighted measurements and inverse-covariance matrices. 
	Gu (2007) proposed a distributed particle filter for Markovian target tracking over an undirected sensor network \cite{gu2007distributed}. Gaussian mixture models (GMM) were adopted to approximate the posterior distribution from weighted particles and the parameters of GMM were exchanged via average consensus filter. 
	Hlinka et al. (2012) proposed a distributed method for computing an approximation of the joint (all-sensors) likelihood function by means of weighted-linear-average consensus algorithm when local likelihood functions belong to the exponential family of distributions \cite{hlinka2012likelihood}. Saptarshi et al. (2014) presented a Bayesian consensus filter that uses logarithmic opinion pool for fusing posterior distributions of the tracked target \cite{bandyopadhyay2014distributed}. Other examples can be found in \cite{julian2012distributed} and \cite{beaudeau2012target}. 
	
	Despite the popularity of statistics dissemination, exchanging statistics can cause high communication burden if the environment to be detected is relatively large in space and complicated in structure. 
	One remedy is to approximate statistics with parametric models, e.g., Gaussian Mixture Model \cite{sheng2005distributed}, which can reduce communication burden to a certain extent. 
	However, such manipulation increases the computation burden of each agent and sacrifices filtering  accuracy due to approximation.
	The measurement dissemination scheme is an alternative solution to address the issue of exchanging large-scale statistics. 
	An early work on measurement dissemination was done by Coates et al. (2004), who used adaptive encoding of observations to minimize communication overhead \cite{coates2004distributed}. Ribeiro et al. (2006) exchanged quantized observations along with error-variance limits considering more pragmatic signal models \cite{ribeiro2006bandwidth}.
	A recent work was conducted by Djuric et al. (2011), who proposed to broadcast raw measurements to other agents, and therefore each agent has a complete set of observations of other agents for executing particle filtering \cite{djuric2011non}.  
	A shortcoming of aforementioned works is that their communication topologies are assumed to be a fixed and complete graph that every pair of distinct agents is constantly connected by a unique edge. 
	In many real applications, the interaction topology can be time-varying due to unreliable links, external disturbances or range limits \cite{xiao2008asynchronous,gao2016robust}.
	In such cases, dynamically changing topologies can cause random packet loss, variable transmission delay, and out-of-sequence measurement (OOSM) issues \cite{xia2009networked}, thus decreasing the performance of distributed estimation.
%	, and even leading to inconsistency and non-consensus. 
	Leung et al. (2010) has explored a decentralized Bayesian filter for dynamic robot networks \cite{leung2010decentralized} in order to achieve centralized-equivalent filtering performance.
	However, it requires the communication of both measurements and statistics, which can still incur large communication overhead.
	
	\textcolor{\revcol}{
	This paper proposes a distributed Bayesian filtering (DBF) method that only uses measurement dissemination for a group of networked UGVs with dynamically changing interaction topologies. 
	In our previous works \cite{liu2017measurement,liu2016distributed,liu2017distributed}, we have proposed a Latest-In-and-Full-Out (LIFO) protocol for measurement exchange and developed a corresponding DBF algorithm.
%	However, it only applies to static targets with simple binary sensor model.
	However, it is only applicable to either tracking moving targets when the interaction topology is time-invariant or to localizing static targets.
	In this work, we substantially extend the previous works and make the following contributions:
	(1) We introduce a new protocol called the Full-In-and-Full-Out (\proto) that allows each UGV to broadcast a history of measurements to its neighbors via single hopping, enabling the localization and tracking of targets using general nonlinear sensor models under time-varying topologies. 
	(2) We propose the 
	\textit{{\fc ness}} condition of the interaction topology and show that, under this condition, {\proto} can disseminate UGVs' measurements over the network within a finite time.
	(3) We develop a FIFO-based distributed Bayesian filter (FIFO-DBF) for each UGV to implement locally.
	A track list is designed to reduce the computational complexity of FIFO-DBF and the communication burden. 
	The FIFO-DBF can avoid the OOSM issue.
	(4) We prove the consistency of FIFO-DBF: each UGV's estimate of target position converges in probability to the true target position asymptotically if the interaction topologies are \textit{\fc.}}
	
	
	The rest of this paper is organized as follows: 
	\Cref{sec:prob} formulates the target tracking problem using multiple UGVs;
	\Cref{sec:\proto} proposes the {\proto} protocol for measurement dissemination in dynamically changing interaction topologies;
	\Cref{sec:\proto-dbf} introduces the FIFO-DBF algorithm and the track list;
	\Cref{sec:consist_proof} proves the consistency of FIFO-DBF;
%	 where the consistency of estimation is proved;
	\Cref{sec:sim} presents simulation results and \Cref{sec:conclu} concludes the paper.